Instant Continuation Marks--Just Add $\lambda$

### 2012-10-02 paper.tex
The list decreases.

\newcommand{\true}{\mathbf{true}}
\newcommand{\false}{\mathbf{false}}
\newcommand{\nil}{\mathbf{nil}}
\newcommand{\pair}[2]{((\mathbf{pair}\,#1)\,#2)}
\newcommand{\eval}[1]{\overline{#1}}

@@

\begin{figure}
\begin{align*}
\true         &= \abs{x}{\abs{y}{x}}\\
\false        &= \abs{x}{\abs{y}{y}}\\
\mathbf{pair} &= \abs{a}{\abs{b}{\abs{z}{\app{\app{z}{a}}{b}}}}\\
\mathbf{fst}  &= \abs{p}{\app{p}{\true}}\\
\mathbf{snd}  &= \abs{p}{\app{p}{\false}}\\
\nil          &= \false
\end{align*}
\label{chuch-encodings}
\caption{Church encodings of booleans and lists}
\end{figure}

@@

The evaluation of operator and operand in an application enlarges the continuation, so marks made within said evaluation will not interfere with pre-existent marks, and this is reflected by the $\false$ flag passed to each. Once the arguments are evaluated, the new context is unnecessary and discarded. The application itself inherits the flag of the original context.

\begin{schemedefn}{\scheme|C[(wcm mark-expr body-expr)]|}
\begin{schemedisplay}
(lambda (flag)
  (lambda (marks)
    ((C[body-expr] TRUE)
     (((lambda (mark-value) (lambda (rest-marks) (lambda (z) C[((z mark-value) rest-marks)])))
       ((C[mark-expr] FALSE) marks))
      ((flag ((C[(SND marks)] (lambda (z) z)) (lambda (z) z))) marks)))))
\end{schemedisplay}
\end{schemedefn}

The definition over \scheme'wcm' expressions is the only one to make explicit use of the value of the flag. Following the evaluation of the mark expression, rule \ref{tail-enforce} is applied, if necessary. The continuity of $\chi$ allows us to construct $\chi(E''[\wcm{v_0}{e_1}])$ from $\chi(E)$ where

\begin{equation}
E''=\begin{cases}
E' &\text{if $E=E'[\wcm{v'}{\hole}]$ for some $E'$ and $v'$}\\
E &\text{otherwise}
\end{cases}
\end{equation}

@@

The simplicity of the definition over \scheme`ccm` expressions offsets the work performed by the other definitions: it simply returns the list passed in.

\begin{definition}
$\C{v_0}=\C{\abs{x}{e'_0}}=\abs{k}{\abs{f}{\abs{m}{\app{k}{\abs{x}{\C{e'_0}}}}}}$
\end{definition}

\begin{definition}
$\C{x}=\abs{k}{\abs{f}{\abs{m}{\app{k}{x}}}}$
\end{definition}

@@

A transformation of this function desugars these constructs into valid JavaScript.
\begin{verbatim}
var fac = function( f, m ) {
    return function( n ) {
        if( n == 0 ) {
            console.log( (function( f, m ) { return m; })( false, m ) );
            return 1;
        }
        else {
            return (function( f, m ) {
                return (function( v ) {
                    return n * fac( false, [ v ].concat( f ? m.slice( 1 ) : m ) )( n - 1 );
                })( n );
            })( f, m );
        }
    }
}
\end{verbatim}

>>>>

\newcommand{\true}{\mathbf{true}}
\newcommand{\false}{\mathbf{false}}
\newcommand{\nil}{\mathbf{nil}}
\newcommand{\cons}[2]{((\mathbf{cons}\,#1)\,#2)}
\newcommand{\eval}[1]{\overline{#1}}

@@

\begin{figure}
\begin{align*}
\true         &= \abs{x}{\abs{y}{x}}\\
\false        &= \abs{x}{\abs{y}{y}}\\
\mathbf{cons} &= \abs{a}{\abs{b}{\abs{z}{\app{\app{z}{a}}{b}}}}\\
\mathbf{snd}  &= \abs{p}{\app{p}{\false}}\\
\nil          &= \false
\end{align*}
\label{chuch-encodings}
\caption{Church encodings of booleans and lists}
\end{figure}

The formal transformation of application follows the \scheme'let' version exactly except the definitions of \scheme'rator-value' and \scheme'rand-value' are folded directly in.

@@

%The evaluation of operator and operand in an application enlarges the continuation, so marks made within said evaluation will not interfere with pre-existent marks, and this is reflected by the $\false$ flag passed to each. Once the arguments are evaluated, the new context is unnecessary and discarded. The application itself inherits the flag of the original context.

The formal transformation of a \scheme'wcm' directive is also extremely similar to the \scheme'let' version. The definition of \scheme'C[cons]' is unfolded and simplified.

\begin{schemedefn}{\scheme|C[(wcm mark-expr body-expr)]|}
\begin{schemedisplay}
(lambda (flag)
  (lambda (marks)
    ((C[body-expr] TRUE)
     (((lambda (mark-value) (lambda (rest-marks) (lambda (z) C[((z mark-value) rest-marks)])))
       ((C[mark-expr] FALSE) marks))
      ((flag Cp[(SND marks)]) marks)))))
\end{schemedisplay}
\end{schemedefn}

%The definition over \scheme'wcm' expressions is the only one to make explicit use of the value of the flag. Following the evaluation of the mark expression, rule \ref{tail-enforce} is applied, if necessary. The continuity of $\chi$ allows us to construct $\chi(E''[\wcm{v_0}{e_1}])$ from $\chi(E)$ where

%\begin{equation}
%E''=\begin{cases}
%E' &\text{if $E=E'[\wcm{v'}{\hole}]$ for some $E'$ and $v'$}\\
%E &\text{otherwise}
%\end{cases}
%\end{equation}

The \scheme'let' version of the transformation of a \scheme'ccm' directive remains unchanged.

@@

%The simplicity of the definition over \scheme`ccm` expressions offsets the work performed by the other definitions: it simply returns the list passed in.

Like other terms, values are modified to receive contextual information. However, it is ignored.
% we use this fact a bit

\begin{schemedefn}{\scheme|C[v]|=\scheme|C[(lambda (x) e)]|}
\begin{schemedisplay}
(lambda (flag)
  (lambda (marks)
    (lambda (x) C[e])))
\end{schemedisplay}
\end{schemedefn}

% Variables have the property that, when substitution occurs, they reconstitute values.

\begin{schemedefn}{\scheme|C[x]|}
\begin{schemedisplay}
(lambda (flag)
  (lambda (marks)
    x))
\end{schemedisplay}
\end{schemedefn}

@@

A transformation of this function desugars these constructs into valid JavaScript.
\begin{verbatim}
var fac = function( flag, marks ) {
    return function( n ) {
        if( n == 0 ) {
            console.log( (function( flag, marks ) { return marks; })( false, marks ) );
            return 1;
        }
        else {
            return (function( flag, marks ) {
                return (function( mark_value, rest_marks ) {
                    return n * fac( false, [ mark_value ].concat( rest_marks ) )( n - 1 );
                })( n, f ? m.slice( 1 ) : m );
            })( flag, marks );
        }
    }
}
\end{verbatim}
